Working memory performance in adverse environments: Enhanced, impaired, or intact?

### 2024-06-25 README.Rmd
new rendering of README file

```{r results ='asis', echo = FALSE}
milestones <- gert::git_tag_list() |> 
  mutate(
    tags = pmap(list(name = name, ref = ref, commit = commit), function(name, ref, commit) {
      gert::git_commit_info(commit) |> 
        as_tibble() |> 
        select(commit = id, author, time, message) 
    })
  ) |> 
  select(-commit, -ref) |> 
  unnest(tags) |> 
  separate(message, into = c("description", "hash", "code"), sep = "\\n") |> 
  mutate(
    branch = gert::git_branch_list() |> filter(local == TRUE) |> pull(name),
    name = map_chr(name, function(name) {
      name |> 
        str_remove("\\d*$") |> 
        str_replace("_", " ") |> 
        str_to_title()
    }),
    code = ifelse(name == "Data Access", str_remove_all(code, "^code\\s") |> str_replace_all(string = _, "\\|\\>", "\\|\\>\\\n"), "Not applicable"),
    link_to_git = ifelse(name == 'Data Access', 
                         paste0(get_git_url(), "/blob/", branch, "/", commit, ".R"),
                         paste0(get_git_url(), "/tree/", commit)
    ),
    hash = ifelse(name != "Data Access", "Not applicable", hash),

    ) |>
  arrange(desc(time))

# Write scripts including code to .projectlog folder
milestones |> 
  pwalk(function(name,commit,author,time,description,hash,code,branch,link_to_git){

    if(name == "Data Access"){
      code <- code |> 
        str_replace_all(string = _, "\\|> ", "\\|>\n") |> 
        str_remove(string = _, "^code ")

      url <- get_git_url() |> 
        paste0("/commit/", commit)

      script <-
        glue(
          "
          ### Date: {time}\n
          ### Description: {description}\n\n
          ### For more information on this commit, see the README file, or go to {url}\n
          ### Below is the full code that was used to access the data:\n\n
          {code}"
        )

      writeLines(script, con = paste0(".projectlog/", commit, ".R"))
    }
  })

# Print milestones
glue_data(milestones, "  - **[{time}]({link_to_git}): {description}**
        - **Milestone:** {name}
        - **Data MD5 hash**: {hash}
        - [Link to code snippet](https://github.com/StefanVermeent/liss_wm_profiles_2023/blob/{branch}/.projectlog/{commit}.R)
        \n
    ")

```

>>>>

```{r results ='asis', echo = FALSE}
milestones <- projectlog::generate_milestone_overview()

milestones
```
